---
title: "Sleepers"
author: "Danijel Kopčinović"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sleepers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(sleepers)
```

# Heading 1
## Heading 2
### Heading 3

--------
********

* Bulleted list
* Item 2
    * Nested bullets need a 4-space indent.
    * Item 2b
* It's possible to put multiple paragraphs of text in a list item.
    
    But to do that, the second and subsequent paragraphs must be
    indented by four or more spaces. It looks better if the first
    bullet is also indented.

1. Item 1.
    * Item a
    * Item b
1. Item 2.


Definition
  : a statement of the exact meaning of a word, especially in a dictionary.
List
  : a number of connected items or names written or printed consecutively,
typically one below the other.
  : barriers enclosing an area for a jousting tournament.

_italic_ or *italic*
__bold__ or **bold**
[link text](destination)<http://this-is-a-raw-url.com>


| Right | Left | Default | Center |
|------:|:-----|---------|:------:|
| 12    | 12   | 12      | 12     |
| 123   | 123  | 123     | 123    |
| 1     | 1    | 1       | 1      |

Notice the use of the : in the spacer under the heading. This determines the alignment of the column.


If the data underlying your table exists in R, don’t lay it out by hand. Instead, use knitr::kable(), or look at printr or pander.

To affect all blocks, call knitr::opts_chunk$set() in a knitr block:
```{r, echo = FALSE}
knitr::opts_chunk$set(
 echo = FALSE,
 warning = FALSE,
 message = FALSE,
 collapse = TRUE, 
 comment = "#>"
)
```


read_sav(system.file("extdata", "experiment_data.sav", package = "sleepers"))
read_sav(system.file("extdata", "survey_data.sav", package = "sleepers"))





